Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
\item Teaching staff wants to have support from their institutions. One of the
  main reasons why this is a factor might be the strict European data
  regulations on data protection; it is very likely that they also want to avoid
  the overhead required to sign up new students every year and other maintenance
  tasks.  In general, additional support with specific formation and access to
  IT help desk for specific features enhance the possibility of a successful
  adoption that improves the learning outcomes. This is supported by the result
  of the two surveys: they prefer whatever ``messaging'' application provided by
  as well as the fact that this application is the ``official'' for the
  university, as shown in Table \ref{tab:interaction}.
\item Teachers require sustainability. The primary rationale is that the
  implementation of changes is costly in terms of effort and prone to mistakes
  during the initial years of deployment of any new technology. Therefore, it is
  logical that if chatbots or messaging platforms are to be introduced, teaching
  staff want this change to be as permanent, and long-term, as possible.
 \item ``Keep it Simple''. Media interaction requirements are simple and only 2.4\%
   of educators are requesting more features. This could be a sign of
   technological burnout produced by the previous pandemic courses, when the
   use of computers significantly increased; however, simplicity is always a
   feature that people want to have in any technology they adopt.
\end{itemize}

>>>>

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
\item Teaching staff wants to have support from their institutions. One of the
  main reasons why this is a factor might be the strict European data
  regulations on data protection; it is very likely that they also want to avoid
  the overhead required to sign up new students every year and other maintenance
  tasks.  In general, additional support with specific training and access to
  IT help desk for specific features enhance the possibility of a successful
  adoption that improves the learning outcomes. This is supported by the result
  of the two surveys: they prefer whatever ``messaging'' application provided by
  as well as the fact that this application is the ``official'' for the
  university, as shown in Table \ref{tab:interaction}.
\item Teachers require sustainability. The primary rationale is that the
  implementation of changes is costly in terms of effort and prone to mistakes
  during the initial years of deployment of any new technology. Therefore, it is
  logical that if chatbots or messaging platforms are to be introduced, teaching
  staff want this change to be as permanent, and long-term, as possible.
 \item ``Keep it Simple''. Media interaction requirements are simple and only 2.4\%
   of educators are requesting more features. This could be a sign of
   technological burnout produced by the previous pandemic courses, when the
   use of computers significantly increased; however, simplicity is always a
   feature that people want to have in any technology they adopt.
\end{itemize}
